### 2014-06-29 Docs/getting_started/getting_started.tex
add rt doc

>>>>

\item {\tt rt} \\ [-3mm]

A Rayleigh-Taylor instability problem.  There are two methods that the
code is run here, in the standard (using {\tt inputs\_2d}), the base state
has the stratified atmosphere and we introduce a velocity perturbation
to start the instability.  The alternate method, {\tt inputs\_2d\_SNe}, uses
the \runparam{do\_smallscale} runtime parameter to eliminate the base state
and instead use the incompressible constraint to evolve the system.
